### 2025-07-01 mixed-models.qmd
20250701 - citations

To visualize the regression coefficients, we can use the `tidy()` function of the `broom.mixed` package, as in @fig-individualFantasyPointsRandomLinearFixedQuadraticSlopesInteractionCoefficients.

@@

To visualize the regression coefficients, we can use the `tidy()` function of the `broom.mixed` package, as in @fig-bayesianRegressionCoefficients.

@@

To visualize the distribution of regression coefficients, we can use the `tidybayes` package, as in @fig-bayesianRegressionCoefficientsDistributions.

>>>>

To visualize the regression coefficients, we can use the `tidy()` function of the `broom.mixed` package [@R-broom.mixed], as in @fig-individualFantasyPointsRandomLinearFixedQuadraticSlopesInteractionCoefficients.

@@

To visualize the regression coefficients, we can use the `tidy()` function of the `broom.mixed` package [@R-broom.mixed], as in @fig-bayesianRegressionCoefficients.

@@

To visualize the distribution of regression coefficients, we can use the `tidybayes` package [@R-tidybayes], as in @fig-bayesianRegressionCoefficientsDistributions.

### 2025-07-01 multiple-regression.qmd
20250701 - citations

If we want to obtain standardized regression coefficients, we can use the `lm.beta()` function of the `QuantPsyc` package.

@@

To visualize the regression coefficients, we can use the `tidy()` function of the `broom` package, as in Figures [-@fig-regressionCoefficients] and [-@fig-regressionCoefficientsStandardized].

>>>>

If we want to obtain standardized regression coefficients, we can use the `lm.beta()` function of the `QuantPsyc` package [R-QuantPsyc].

@@

To visualize the regression coefficients, we can use the `tidy()` function of the `broom` package [@R-broom], as in Figures [-@fig-regressionCoefficients] and [-@fig-regressionCoefficientsStandardized].

### 2025-07-01 simulation.qmd
20250701 - citations

You can generate a template for Monte Carlo simulations in the `SimDesign` [@R-SimDesign; @Chalmers2020] package using the following code:

@@

>>>>

You can generate a template for Monte Carlo simulations in the `SimDesign` [@R-SimDesign; @Chalmers2020_packages] package using the following code:

@@

For each player, we identify the optimal distribution as either a normal distribution , or as a skew-normal distribution.
The normal distribution was fit using the `fitdist()` function of the `fitdistrplus` package [@R-fitdistrplus; @DelignetteMuller2015_packages].
The skew-normal distribution was fit using the `selm()` function of the `sn` package [@R-sn; @Azzalini2023_packages].
